Quotient maps and configuration spaces of hard disks

### 2022-02-09 manuscript/main.tex
base config space definition added in sec.2

The configuration space of $n$ points on a torus $T^2$ is the product space of $n$ toruses, or 
\begin{equation*}
\Lambda(n) = \{ \config{x} = (\vec{x}_1, \dots ,\vec{x}_n) \;\vert\; \vec{x}_i \in T^2 \}.
\label{eq:configuration_space1}
\end{equation*}
Figure \ref{fig:figure2} shows the square and hexagonal toruses used in this study; periodic boundary conditions are imposed by identifying opposite edges of both domains. Two domains are studied to help separate the specific and general phenomena that can occur when quotienting a configuration space by the action of a symmetry group. More generally, any numerical study of the Topological Hypothesis for the hard disk system will require a choice of domain, and it will be necessary to distinguish what are consequences of that choice and what are nascent features of the thermodynamic system.

>>>>

The configuration space of $n$ points on a torus $T^2$ is the product space of $n$ toruses, or 
\begin{equation*}
\Lambda(n) = \{ \config{x} = (\vec{x}_1, \dots ,\vec{x}_n) \;\vert\; \vec{x}_i \in T^2 \}.
\label{eq:configuration_space1}
\end{equation*}
\red{$\Lambda(n)$ is also called the base configuration space as all other spaces considered in this work are originated from it.} Figure \ref{fig:figure2} shows the square and hexagonal toruses used in this study; periodic boundary conditions are imposed by identifying opposite edges of both domains. Two domains are studied to help separate the specific and general phenomena that can occur when quotienting a configuration space by the action of a symmetry group. More generally, any numerical study of the Topological Hypothesis for the hard disk system will require a choice of domain, and it will be necessary to distinguish what are consequences of that choice and what are nascent features of the thermodynamic system.
